---
title: "Warfarin Dosing Service"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(edwr)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(dygraphs)
library(xts)

data.raw <- "../data/raw"

# get all warfarin and consult orders
data.orders <- read_data(data.raw, "orders") %>%
    as.order_by() %>%
    filter(action.type == "Order") %>%
    mutate(action.date = floor_date(action.datetime, unit = "day"),
           consult = !str_detect(order, "^warfarin$"))

# make tidy data set
df <- data.orders %>%
    distinct(pie.id, action.date, consult) %>%
    group_by(pie.id, action.date) %>%
    mutate(value = TRUE,
           consult = if_else(consult == TRUE, "consult", "warfarin")) %>%
    spread(consult, value) %>%
    mutate(warfarin = if_else(consult == TRUE & is.na(warfarin), TRUE, warfarin)) %>%
    gather(order, value, consult, warfarin) %>%
    filter(!is.na(value)) %>%
    group_by(pie.id, action.date, order) %>%
    summarize(n = n()) %>%
    group_by(action.date, order) %>%
    summarize(n = n()) %>%
    spread(order, n) %>%
    mutate(warfarin = if_else(is.na(consult), warfarin, warfarin - consult)) %>%
    gather(order, n, -action.date) %>%
    mutate(n = coalesce(n, 0L)) %>%
    spread(order, n) 

ts <- as.matrix(df[, 2:3]) %>% as.xts(order.by = df$action.date, tzone = "US/Central")

dyg <- dygraph(ts, main = "Daily Warfarin Orders") %>%
    dySeries("consult", label = "Pharmacy") %>%
    dySeries("warfarin", label = "Traditional") 
```

Smoothed
========================================================

### Utilization of Pharmacy Warfarin Dosing Service

```{r}
dyg %>%
    dyOptions(colors = RColorBrewer::brewer.pal(3, "Set1")) %>%
    dyRoller(rollPeriod = 30)
```

> Data presented as the average over a rolling period of days. The rolling period can be adjusted using the text box in the lower left corner of the figure.

Range
========================================================

### Utilization of Pharmacy Warfarin Dosing Service

```{r}
dyg %>%
    dyOptions(colors = RColorBrewer::brewer.pal(3, "Set1"), fillGraph = TRUE, fillAlpha = 0.4) %>%
    dyRangeSelector(dateWindow = c("2015-07-01", "2015-12-31"))
```

> Data presented as actual daily values. Adjust the time period being displayed using the selector at the bottom of the figure.

Totals
========================================================

### Total Daily Utilization of Warfarin

```{r}
dyg %>%
    dyOptions(stackedGraph = TRUE, colors = RColorBrewer::brewer.pal(3, "Set1")) %>%
    dyRangeSelector(dateWindow = c("2015-07-01", "2015-12-31"))
```

> Data is stacked to represent total number of daily warfarin orders during the selected time period.
