---
title: "Warfarin Dosing Service"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(edwr)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(dygraphs)
library(xts)
library(RColorBrewer)
library(plotly)
library(d3heatmap)

data.raw <- "../data/raw"

date.start <- c("2016-01-01", "2016-06-30")

# get all warfarin and consult orders
data.orders <- read_data(data.raw, "orders") %>%
    as.order_by() %>%
    filter(action.type == "Order") %>%
    mutate(action.date = floor_date(action.datetime, unit = "day"),
           consult = str_detect(order, "Dosing"))

# make tidy data set
df <- data.orders %>%
    distinct(pie.id, action.date, consult) %>%
    group_by(pie.id, action.date) %>%
    mutate(value = TRUE,
           consult = if_else(consult == TRUE, "consult", "warfarin")) %>%
    spread(consult, value) %>%
    mutate(warfarin = if_else(consult == TRUE & is.na(warfarin), TRUE, warfarin)) %>%
    gather(order, value, consult, warfarin) %>%
    filter(!is.na(value)) %>%
    group_by(pie.id, action.date, order) %>%
    summarize(n = n()) %>%
    group_by(action.date, order) %>%
    summarize(n = n()) %>%
    spread(order, n) %>%
    mutate(warfarin = if_else(is.na(consult), warfarin, warfarin - consult)) %>%
    gather(order, n, -action.date) %>%
    mutate(n = coalesce(n, 0L)) %>%
    spread(order, n) 

ts <- as.matrix(df[, 2:3]) %>% 
    as.xts(order.by = df$action.date, tzone = "US/Central")

dyg <- dygraph(ts, main = "Daily Warfarin Orders") %>%
    dySeries("consult", label = "Pharmacy") %>%
    dySeries("warfarin", label = "Traditional") 
```

Utilization
========================================================

### Utilization of Pharmacy Warfarin Dosing Service

```{r}
dyg %>%
    dyOptions(colors = brewer.pal(3, "Set1")) %>%
    dyRoller(rollPeriod = 15) %>%
    dyRangeSelector()
```

> Data presented as the average over a rolling period of days (default is 15). The rolling period can be adjusted using the text box in the lower left corner of the figure. Set the value to 1 to show individual daily values. Adjust the time period being displayed using the selector at the bottom of the figure.

Orders by Unit
========================================================

Column {.tabset}
--------------------------------------------------------

### Annual Consults by Hospital Unit

```{r}

unit.list <- list("HH 3CIM" = "HH 3CP", 
                  "HH 3ECP" = "HH 3CP", 
                  "HH 3WCP" = "HH 3CP", 
                  "HH 4HVI CIMU" = "HVI CIMU", 
                  "Jones 6 West" = "HH 6JP",
                  "HH 3JSP" = "HH 3JP",
                  "HH 5ECP" = "HH 5CP",
                  "HH 5WCP" = "HH 5CP",
                  "HH WCAN" = "HH WC6N",
                  "HH 5EJP" = "HH 5JP",
                  "HH 5WJP" = "HH 5JP",
                  "HH 6EJP" = "HH 6JP",
                  "HH 6WJP" = "HH 6JP",
                  "HH 8NJP" = "HH 8JP",
                  "HH 8WJP" = "HH 8JP",
                  "HH 9EJP" = "HH 9JP",
                  "HH 9WJP" = "HH 9JP")

units <- data.orders %>%
    filter(consult == TRUE) %>%
    distinct(pie.id, order.unit, action.date) %>%
    mutate(action.year = floor_date(action.date, "year"),
           year = as.numeric(year(action.year)),
           order.unit = str_replace_all(order.unit, unit.list)) %>%
    group_by(order.unit, year) %>%
    summarize(consults = n()) %>%
    ungroup() %>%
    mutate(order.unit = coalesce(order.unit, "Other")) %>%
    spread(year, consults, fill = 0)

tmp <- as.matrix(units[, -1])
rownames(tmp) <- units$order.unit

d3heatmap(tmp, scale = "column", colors = "OrRd", dendrogram = "none")
```

### Rolling 6-Month Consults by Unit

```{r}
units.month <- data.orders %>%
    filter(consult == TRUE) %>%
    distinct(pie.id, order.unit, action.date) %>%
    mutate(action.month = floor_date(action.date, "month"),
           # year = as.numeric(year(action.year)),
           order.unit = str_replace_all(order.unit, unit.list)) %>%
    filter(action.month >= max(action.month) - months(6)) %>%
    group_by(order.unit, action.month) %>%
    summarize(consults = n()) %>%
    ungroup() %>%
    mutate(order.unit = coalesce(order.unit, "Other")) %>%
    spread(action.month, consults, fill = 0)

tmp <- as.matrix(units.month[, -1])
rownames(tmp) <- units.month$order.unit

d3heatmap(tmp, scale = "column", colors = "OrRd", dendrogram = "none")

```

Dosing
========================================================

Column {.tabset}
--------------------------------------------------------

### Initial Warfarin Dose

```{r}
ref <- data_frame(name = "warfarin", type = "med", group = "sched")

data.warfarin <- read_data(data.raw, "meds") %>%
    as.meds_sched() %>%
    tidy_data(ref = ref) %>%
    group_by(pie.id) 

warf.duration <- data.warfarin %>%
    summarize(warf.start = first(med.datetime),
              warf.stop = last(med.datetime))

warf.doses <- data.warfarin %>%
    mutate(med.date = floor_date(med.datetime, "day"),
           warf.month = floor_date(med.datetime, "month"),
           warf.year = floor_date(med.datetime, "year"),
           warf.day = as.numeric(difftime(med.date, first(med.date), units = "days"))) %>%
    group_by(pie.id, warf.year, warf.month, warf.day) %>%
    summarize(dose = sum(as.numeric(med.dose))) 

ds.pts <- data.orders %>%
    filter(consult == TRUE) %>%
    distinct(pie.id) %>%
    mutate(pharmacy = TRUE)

high.dose <- warf.doses %>%
    ungroup %>%
    filter(dose > 20) %>%
    distinct(pie.id)

doses <- warf.doses %>%
    filter(!(pie.id %in% high.dose$pie.id)) %>%
    left_join(ds.pts, by = "pie.id") %>%
    mutate(group = if_else(pharmacy == TRUE, "Pharmacy", "Traditional", "Traditional"),
           year = as.character(year(warf.year)))

# add indication
first.dose <- doses %>%
    # mutate(year = as.character(year(warf.year))) %>%
    group_by(pie.id, year, group) %>%
    summarize(dose = first(dose)) %>%
    group_by(group, year)
    
plot_ly(data = first.dose, x = ~group, y = ~dose, color = ~factor(year), colors = "Set1") %>%
    add_boxplot() %>%
    layout(boxmode = "group",
           xaxis = list(title = "Group"),
           yaxis = list(title = "Initial Warfarin Dose (mg)"))
```

### Annual Daily Dose

```{r}
df <- doses %>%
    filter(warf.day %in% 0:10) %>%
    group_by(group, year, warf.day) %>%
    summarize(dose.mean = mean(dose, na.rm = TRUE),
              dose.sd = sd(dose, na.rm = TRUE),
              dose.sem = dose.sd / sqrt(length(dose)),
              num.pts = n()) %>%
    ungroup() %>%
    arrange(group, year, warf.day) %>%
    group_by(group, year)

plot_ly(data = df, 
        x = ~warf.day, 
        y = ~dose.mean, 
        colors = "Set1",
        hoverinfo = "text", 
        text = paste(df$group, "<br> n = ", df$num.pts, "<br> day = ", df$warf.day, "<br> mean dose = ", round(df$dose.mean, 1))) %>%
    add_markers(symbol = ~group) %>%
    add_lines(color = ~year) %>%
    layout(xaxis = list(title = "Days of Warfarin"),
           yaxis = list(title = "Mean Warfarin Dose (mg)"))
```

### Rolling 6-Month Daily Dose

```{r}
df <- doses %>%
    ungroup() %>%
    filter(warf.day %in% 0:10,
           warf.month >= max(warf.month) - months(6)) %>%
    group_by(group, warf.day) %>%
    summarize(dose.mean = mean(dose, na.rm = TRUE),
              dose.sd = sd(dose, na.rm = TRUE),
              dose.sem = dose.sd / sqrt(length(dose)),
              num.pts = n()) %>%
    ungroup() %>%
    arrange(group, warf.day) %>%
    group_by(group)

plot_ly(data = df, 
        x = ~warf.day, 
        y = ~dose.mean, 
        colors = "Set1",
        hoverinfo = "text", 
        text = paste(df$group, "<br> n = ", df$num.pts, "<br> day = ", df$warf.day, "<br> mean dose = ", round(df$dose.mean, 1))) %>%
    add_lines(color = ~group) %>%
    add_markers(color = ~group, size = ~num.pts) %>%
    layout(xaxis = list(title = "Days of Warfarin"),
           yaxis = list(title = "Mean Warfarin Dose (mg)"))

```

INR
========================================================

Column {.tabset}
--------------------------------------------------------

### Annual Mean INR

```{r}
data.coags <- read_data(data.raw, "labs_coag") %>%
    as.labs() %>%
    select(-`Clinical Event Result Type`) %>%
    tidy_data() %>%
    inner_join(warf.duration, by = "pie.id") %>%
    filter(lab == "inr",
           lab.datetime >= floor_date(warf.start, "day") - days(1),
           lab.datetime <= ceiling_date(warf.stop, "day") + days(1)) %>%
    arrange(pie.id, lab.datetime) %>%
    mutate(
        warf.day = as.numeric(difftime(
            floor_date(lab.datetime, "day"), 
            floor_date(warf.start, "day"), 
            units = "days")),
        warf.month = floor_date(warf.start, "month"),
        warf.year = floor_date(warf.start, "year")) %>%
    group_by(pie.id, warf.year, warf.month, warf.day) %>%
    summarize(inr = max(lab.result))

inr.first <- data.coags %>%
    group_by(pie.id) %>%
    filter(warf.day <= 0) %>%
    summarize(inr.first = last(inr))

d <- data.coags %>%
    left_join(ds.pts, by = "pie.id") %>%
    mutate(group = if_else(pharmacy == TRUE, "pharmacy", "traditional", "traditional"),
           year = as.character(year(warf.year))) %>%
    # left_join(inr.first, by = "pie.id") %>%
    # mutate(inr.change = inr - inr.first) %>%
    filter(warf.day %in% 0:10) %>%
    # mutate(warf.day = as.character(warf.day)) %>%
    group_by(group, year, warf.day) %>%
    summarize(inr.mean = mean(inr, na.rm = TRUE),
              inr.sd = sd(inr, na.rm = TRUE),
              inr.sem = inr.sd / sqrt(length(inr)),
              num.pts = n()) %>%
    ungroup() %>%
    arrange(group, year, warf.day) %>%
    group_by(group, year)

plot_ly(data = d, 
        x = ~warf.day, 
        y = ~inr.mean, 
        colors = "Set1",
        hoverinfo = "text", 
        text = paste(d$group, "<br> n = ", d$num.pts, "<br> day = ", d$warf.day, "<br> mean INR = ", round(d$inr.mean, 2))) %>%
    add_markers(symbol = ~group) %>%
    add_lines(color = ~year) %>%
    layout(xaxis = list(title = "Days of Warfarin"),
           yaxis = list(title = "Mean INR"))

```

### Rolling 6-Month Mean INR

```{r}
d <- data.coags %>%
    left_join(ds.pts, by = "pie.id") %>%
    mutate(group = if_else(pharmacy == TRUE, "pharmacy", "traditional", "traditional")) %>%
    ungroup() %>%
    filter(warf.day %in% 0:10,
           warf.month >= max(warf.month) - months(6)) %>%
    group_by(group, warf.day) %>%
    summarize(inr.mean = mean(inr, na.rm = TRUE),
              inr.sd = sd(inr, na.rm = TRUE),
              inr.sem = inr.sd / sqrt(length(inr)),
              num.pts = n()) %>%
    ungroup() %>%
    arrange(group, warf.day) %>%
    # mutate(warf.month = as.character(warf.month)) %>%
    group_by(group)

plot_ly(data = d, 
        x = ~warf.day, 
        y = ~inr.mean, 
        colors = "Set1",
        hoverinfo = "text", 
        text = paste(d$group, "<br> n = ", d$num.pts, "<br> day = ", d$warf.day, "<br> mean INR = ", round(d$inr.mean, 2))) %>%
    add_lines(color = ~group) %>%
    add_markers(color = ~group, size = ~num.pts) %>%
    layout(xaxis = list(title = "Days of Warfarin"),
           yaxis = list(title = "Mean INR"))
```


